\documentclass[12pt, oneside]{article}   	
\usepackage{geometry}                		
\geometry{letterpaper}                   		

\usepackage{graphicx}		
\usepackage{amssymb}

\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{Group 3:\\
		Shuying, Chen
		400080161\\
		Ace, Huang
		400051063
		\\
		Guiye, Wu
		400089784
		}
\rhead{\today}

\author{}

\begin{document}

\marginpar{}
\section*{Minesweeper: Problem Statement}
\subsection*{Introduction}

\newcommand*\apos{\textsc{\char13}}
Recently, young people are coming back to pursuit the classical style in every corners of our lives.Game companies are re-creating their new games into 8-bit old styles in order to cherish the old memory. Today, our group is managing to bring back the classical Windows XP minesweeper and we are designing so that it can be run on both linux and windows system, with a brand new outlookings and some new features, as a result, bring out the same but better feelings to the players.

\subsection*{Importance}

For the most classic minesweeper game, it was initially an included game on the  Windows Operating System, which is no longer available. This game was once to be one of the most popular game, had been held several competitions and became a good way of relaxing in the leisure time. However, the variety, high replayability and attraction of new games made people start to forget the classic ones.

With re-implementing a new version to the classic minesweeper, we hope to catch people’s attention back to this old school classic puzzle game, which can entertain players and improve the logical thinking in the meantime. 


\subsection*{Context}

The original Minesweeper is classic and orthodox, we are trying to redevelop the game with a new style of the user interface with some funny features to increase the enjoyment. The game is written in python and will be an offline software, which pre-downloading is required. It will create an environment that allows users to play the game anytime with or without internet. The game is very suitable for those people who want to challenge the puzzle that clears out all the traps, however, the game is for all ages, since the game does provide several difficulty levels. Also, we will apply hints and strategy to make the game easy and fun for the new players. 

\end{document}  
%% The project sturcuture is referenced from URL: https://gitlab.cas.mcmaster.ca/theateam/FloppyFishGroup/blob/master/Game/documentation/Revision0/problemStatement/Latex+Extras/ProblemStatement.tex