\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}


\title{Development Plan}

\author{Team 3\\
        Shuying Chen, 400080161\\
        Ziyang Huang, 400051063\\
        Guiye Wu, 400089784
}
\date{September 2018}
\begin{document}
\maketitle
\newpage



\tableofcontents
\newpage

\section{Team Information}

Team Name: Banana Boat\\
Team Members: 

\begin{table}[h!]
    \begin{center}
	\begin{tabular}{|p{5.0cm}|p{5.0cm}|}
	\hline
	\textbf{Name} & \textbf{MacId}\\
	\hline
      Shuying Chen &  chens121\\
      \hline
      Ziyang Huang& huang60\\
      \hline
      Guiye Wu & wug13\\
      \hline
	\end{tabular}
    \end{center}
	\end{table}
	\renewcommand{\arraystretch}{1}
\newpage
\section{Team Meeting Plan}
    %\begin{table}[h!]
	\begin{center}
	\begin{tabular}{|p{1.5cm}|p{2.0cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
	\hline
	\textbf{Date} & \textbf{Location} & \textbf{Time} & \textbf{Content} & \textbf{Document}\\
	\hline
    Sep 9-15 & Student Center & Sep 10 17:00-17:15 & team formation & \\
    \hline
    Sep 16-22 & Mills Library & Sep 18 16:30-17:45& Problem Statement Rev 0& Problem Statemen.tex\\
      \hline
    Sep 23-29 & Mills Library & Sep 25 16:30-18:30& Development Plan Rev 0& Devlopment Plan 0.tex\\
      \hline
    Sep 30- Oct 6 & Mills Library & Oct 2 17:30-19:00& Requirements document rev0&Requirements Doc 0 \\
      \hline
    Oct 7-13 & Mills Library & Oct 10 17:30-18:30& Proof of concept demonstration& \\
      \hline
    Oct 14-20 & Mills Library & Oct 17 17:30-18:30 & Proof of concept demonstration& \\
      \hline
    Oct 20-27 & Mills Library & Oct 23 17:30-18:30 & Testing and Debugging& \\
      \hline
    Oct 28-Nov 3 & Mills Library & Nov 1 17:30-18:30 & Test plan rev0& \\
      \hline
    Nov 4-10 & Mills Library & Nov 7 17:30-18:30 & Design and Document rev0& \\
      \hline
    Nov 11-17 & Mills Library & Nov 14 17:30-18:30& Rev0 demonstration& \\
      \hline
    Nov 18-24 & Mills Library & Nov 21 17:30-18:30& Final demonstration Preparation and peer evaluation& \\
      \hline
    Nov 25-Dec 2 & Mills Library & Nov 28 17:30-18:30 & Final Documentation& \\
      \hline
    Dec 2-8 & Mills Library & Dec 5 17:30-18:30& Final Documentation& \\
      \hline
      
	\end{tabular}
    %\caption{table 2: Meeting Plan}
	\end{center}
    %\end{table} 
Rules for agenda: we will have a template for the meeting minutes and one of the member will take the notes and update a new meeting minutes every time to keep in track with the meeting plan.
\newpage

\section{Team Communication Plan}
    We will use emails and messenger to communicate with each other. We have exchanged our contact information so that we are able to communicate with each other about everything that is relative to our project.

\newpage

\section{Team Member Roles}
    Team Leader: Shuyin Chen\\
	Team Member: Ace Huang, Guiye Wu \\
	Scribe: All of the members(one at each time)
	will do the process documentation and Gantt Chart uploading.

\newpage

\section{Git Work-flow Plan}
1. Create a new branch(for the use of merging and bug fixing).\\
2. Do any addition or modification in the new branch.\\
3. If everything in the new branch work correctly, merge with the master branch.\\
4. Use the issues on the git-lab to show our discussion results of important issues, bugs or milestones(descriptions of the big events).\\
\\
Every submission of milestones or any modification of files or adding tags are able to be done in above steps.
\newpage
\section{Proof of Concept Demonstration Plan}

    The program "minesweeper" should be available and feasible for us to use python to re-develop it. The user interface will be the hardest part of the implementation, the original code was written in java, which using GUI to implement the user interface. We are planning to re-implement this project in python. Unfortunately, we are not very familiar with how to create user interface with python, so this will be a challenge for the project. 
    We will make a simple user interface for the initial implementation and try to refine the interface step by step. The customization is necessary for us while re-develop the program. We will add some more customized features(outlooks, functions) that based on the custom feedback and tests.
      

\newpage

\section{Technology}
    language: python
	\\IDE: python idle
	\\test framework: Unit Testing - PyTest
	\\document Generation: Latex and Doc; We will using overleaf and GOOGLE DOC as supporting tool for the team member to work together on the documentation

\newpage

\section{Coding Style}
We will focus on one python style for coding which reference to\\ https://google.github.io/styleguide/pyguide.html
\newpage

\section{Project Schedule}
Project schedule refers to GanttProject file, and the file will be updated each time after the meeting(or if the work is done). All milestones and the roles assignment are in GanttProject file, roles are separated equally and every of us will follow the roles to finish the corresponding work on time.

\newpage

\section{Project Review}

\end{document}
   